Block bootstrap consistency\\under weak assumptions

### 2015-12-31 subs/ETr2/reply_2.tex

>>>>

$\hat{W}_n(\gamma)$ should have been defined as
\begin{equation*}
\hat{W}_n(\gamma) = \sqrt{\tfrac{\gamma}{n}} \sum_{t=1}^{\lfloor \gamma n \rfloor}
(X_{nt} - \bar{\mu}_n) / \hat{\sigma}_n(\gamma),
\end{equation*}
would make the limit a Wiener process and (I think) would have
prevented a lot of your confusion. In any case, I have merged this
corollary with the previous theorem (Theorem 2) and have edited the
surrounding text to make this part more clear. I have also removed the
conditions for normalizing partial sums that would not converge to a
Wiener processes and left that element implicit.
